---
title: "social nets  models"
output:
  html_document:
    df_print: paged
    code_folding: hide
editor_options:
  chunk_output_type: inline
---

This Rmd runs all the mixed models using the data from recoding covariates longitudinal.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
library(stargazer)
library(mice)
library(ggplot2)
library(tableone)
library(kableExtra)
library(tidyverse)
```


```{r make table}
#function to make table of coefficients
make_table <- function(model){
  coef <- summary(model)$coef[2]
  confint <- data.frame(confint(model))

  colnames(confint) = c("conf.low", "conf.high")

  table_out <- round(cbind(coef, confint[4,]),3)

  table_out <- table_out %>%
    unite(CI, conf.low, conf.high, sep = ",") %>%
    mutate(CI = paste0("(", CI, ")")) %>%
    unite(coef, coef, CI, sep = " ")
}
```

## Datasets
```{r datasets}
final_dat_both <- read.csv("/Users/ccalmasini/Desktop/Projects/social_networks_paper/social_nets_dat_both_waves.csv")

#centering education at 12 and age at 65
#turning variables into factors
#dropping nas for complete case analysis
khandle1 <- final_dat_both %>%
  mutate(W1_EDU_new_c = W1_EDU_new - 12,
         W1_D_GENDER = factor(case_when(W1_D_GENDER == 1 ~ "Male",
                                        W1_D_GENDER == 2 ~ "Female")),
         W1_SMK = ifelse(W1_SMK == 0, "No", "Yes"),
         years_over_65 = W1_INTERVIEW_AGE - 65) %>%
  drop_na(W1_EDU_new_c, income_num, ADL_IADL, tot_drinks_week, retirement_stat)

#turning data into long format
#each person is repeated 3 times: one for execz, one for vrmemz an and one for semz
#make a r_d variable which combines race and cognitive domain
khandle1_long <- khandle1 %>%
  mutate(#income_num_c = scale(income_num, center = TRUE, scale = TRUE),
         income_num_c = log(income_num)) %>%
  gather(cognitive_test, cognitive_score, c(execz, vrmemz, semz)) %>%
  mutate(cognitive_test =  as.factor(cognitive_test),
         STUDYID = as.factor(STUDYID)) %>%
  unite(r_d, W1_D_RACE_SUMMARY, cognitive_test, remove = FALSE) %>%
  mutate(r_d = relevel(as.factor(r_d), ref = "Asian_execz"))
```

# Integration score models

## Testing for linearity

Test that there is a linear relationship between integration score and cognitive score by including integration score as a categorical variable. 

```{r}
khandle1_long <- khandle1_long %>%
  mutate(int_score_cat = as.factor(int_score))

m_linear <- lmerTest::lmer(cognitive_score ~ int_score_cat + r_d + poly(years_over_65, 2, raw = TRUE) + W1_D_GENDER +
                       W1_EDU_new_c + (1|STUDYID), 
                     REML = FALSE, 
                     data = khandle1_long)

stargazer(summary(m_linear)$coef, type = "text", title = "Testing for linearity")

# this just saves the table 
stargazer(summary(m_linear)$coef, 
          type = "html", 
          title = "Testing for linearity",
          out = "/Users/ccalmasini/Desktop/Projects/social_networks_paper/Tables/linearity_test.html")

```

## F-test 

The first step in the analysis is to test whether we can estimate a single effect of social integration on all 3 cognitive domains. Run a model with an interaction between integration score and race/domain combination and perform F test.

```{r F test}
#this model is to test whether we can estimate a single effect for all race/domain combinations
m1 <- lmerTest::lmer(cognitive_score ~ int_score * r_d + poly(years_over_65, 2, raw = TRUE) + W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                     REML = FALSE, data = khandle1_long)

#f-test for the  int_score*r_d interaction term is not significant
anova(m1)

#checking for individual comparisons, int_score*asian_vrmem is significant
stargazer(summary(m1)$coef, type = "text")
```

## Main covariates (age, gender, education, race)

### Full sample model (adjusting for asian * vrmem)

```{r full sample main}
#create asian_vrmemz indicator
khandle1_long <- khandle1_long %>%
  mutate(asian_vrmemz = as.factor(ifelse(r_d == "Asian_vrmemz", 1, 0)))

#overall model
m1_main <- lmerTest::lmer(cognitive_score ~ int_score + r_d + int_score:asian_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                       REML = FALSE, data = khandle1_long)

stargazer(summary(m1_main)$coef, type = "text")

#this just gives the coefficient for int_score with 95%CI
table1 <- make_table(m1_main)
saveRDS(table1, 'output/tablem1.RDS')

#diagnostic plots
plot(m1_main)
qqnorm(residuals(m1_main))

#adding interaction between integration score and race
m1_int <- lmerTest::lmer(cognitive_score ~ int_score + r_d + int_score:W1_D_RACE_SUMMARY + 
                           int_score:asian_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                       REML = FALSE, data = khandle1_long)

anova(m1_int)
stargazer(summary(m1_int)$coef, type = "text")

# this is another way to code the interaction between integration score and race

t2 <- khandle1_long %>% 
  mutate(wh = ifelse(W1_D_RACE_SUMMARY == "White", 1, 0),
         bl = ifelse(W1_D_RACE_SUMMARY == "Black", 1, 0),
         la = ifelse(W1_D_RACE_SUMMARY == "LatinX", 1, 0),
         as = ifelse(W1_D_RACE_SUMMARY == "Asian", 1, 0),
         int_wh = wh*int_score,
         int_bl = bl*int_score,
         int_la = la*int_score,
         int_as = as*int_score)

t_mod <- lmerTest::lmer(cognitive_score ~ int_score + r_d + int_wh + int_bl + int_la + int_as + 
                           int_score:asian_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                       REML = FALSE, data = t2)

t_mod_small <- lmerTest::lmer(cognitive_score ~ int_score + r_d + 
                           int_score:asian_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                       REML = FALSE, data = t2)
summary(t_mod)
anova(t_mod_small, t_mod)
```

### Stratified by race

```{r stratified, main covars}
#This runs the model for integration score by race
#For Asian, need to include the int_score:asian_vrmemz interaction to exclude this group from the interpretation of the main int_score coefficient
tables_main_covars <- list()
for(i in c("White", "Black", "LatinX", "Asian")){
  if (i != "Asian"){
    mod <- lmerTest::lmer(cognitive_score ~ int_score + poly(years_over_65, 2, raw = TRUE) + 
                                        r_d + W1_D_GENDER + W1_EDU_new_c + (1 |STUDYID), REML = FALSE, data = khandle1_long, subset = (W1_D_RACE_SUMMARY == i))
  } else {
    mod <- lmerTest::lmer(cognitive_score ~ int_score + poly(years_over_65, 2, raw = TRUE) + int_score:asian_vrmemz + 
                                        r_d  + W1_D_GENDER + W1_EDU_new_c + (1 |STUDYID), REML = FALSE, data = khandle1_long, subset = (W1_D_RACE_SUMMARY == i))
  }
  
  stargazer(summary(mod)$coef, type = "text", title = paste("Regression for", i,  "participants - integration score, main covariates"))
  
  tables_main_covars[[i]] <- make_table(mod)
}

saveRDS(tables_main_covars, 'output/tables_main_covars.RDS')
```

------------

## Using all covariates (ADL_IADL, alcohol, income, retirement status)

### Full sample

```{r overall & all covs}
#this is overall model also including other covariates
m2 <- lmerTest::lmer(cognitive_score ~ int_score + r_d + int_score:asian_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID), 
                       REML = FALSE, data = khandle1_long)

stargazer(summary(m2)$coeff, type = "text")

table2 <- make_table(m2)
saveRDS(table2, 'output/tablem2.RDS')

#adding interaction between int score and race to check whether effect varies by race
m2_int <- lmerTest::lmer(cognitive_score ~ int_score + r_d + int_score:W1_D_RACE_SUMMARY + 
                           int_score:asian_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID), 
                       REML = FALSE, data = khandle1_long)
anova(m2_int)

stargazer(summary(m2_int)$coef, type = "text")
```

### Stratified

```{r}
#This for-loop is the same as above, but using the enhanced covariate sets
tables_all_covars <- list()
for(i in c("White", "Black", "LatinX", "Asian")){
  if(i != "Asian"){
    mod_all <- lmerTest::lmer(cognitive_score ~ int_score + poly(years_over_65, 2, raw = TRUE) + r_d + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID), 
                       REML = FALSE, data = khandle1_long, subset = (W1_D_RACE_SUMMARY == i))
  
  } else {
    mod_all <- lmerTest::lmer(cognitive_score ~ int_score + poly(years_over_65, 2, raw = TRUE) + int_score:asian_vrmemz +  r_d + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID), 
                       REML = FALSE, data = khandle1_long, subset = (W1_D_RACE_SUMMARY == i))
  }
  
  stargazer(summary(mod_all)$coef, 
            mod_all,
            ci = T,
            type = "text", 
            title = paste("Regression for", 
                          i,  
                          "participants -- integration score, enhanced covariates"))
  
  tables_all_covars[[i]] <- make_table(mod_all)
}

saveRDS(tables_all_covars, 'output/tables_all_covars.RDS')
```

## Confidante 

This part of the code runs the models using confidante as the main independent variable instead of integration score

### F-test
```{r}
table(khandle1$confidante_bin)

#confidante - f test
m_confidante <- lmerTest::lmer(cognitive_score ~ confidante_bin*r_d + poly(years_over_65, 2, raw = TRUE) + 
                         W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                         REML = FALSE, data = khandle1_long)
anova(m_confidante)

stargazer(summary(m_confidante)$coeff, type = "text")
```

## Adjusting for asian vrmem and latinx vrmemz (main covariates)
### Full sample
```{r main conf overall}
khandle1_long <- khandle1_long %>%
  mutate(latin_vrmemz = as.factor(ifelse(r_d == "LatinX_vrmemz", 1, 0)))

m_main_confidante_overall <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:asian_vrmemz + 
                                         confidante_bin:latin_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                                         W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                                       REML = FALSE, data = khandle1_long)

stargazer(summary(m_main_confidante_overall)$coef, 
          type = "text", 
          title = "Confidante regression for full sample using main covars")

table1_confi <- make_table(m_main_confidante_overall)
saveRDS(table1_confi, 'output/table1_confi.RDS')

#adding interaction between confidante and race
m1_int_confi <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:W1_D_RACE_SUMMARY + 
                           confidante_bin:asian_vrmemz + confidante_bin:latin_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                       REML = FALSE, data = khandle1_long)
anova(m1_int_confi)
```

### Confidante models stratified by race and adjusted for main covars

```{r confidante, main covars, stratified}
#this runs the stratified models with main covariates
#all models for asian should include confidante_bin x asian_vrmemz interaction
#all models for latino should include confidante_bin x latin_vrmemz interaction

tables_main_covars_confi <- list()

for(i in c("White", "Black", "LatinX", "Asian")){
  if(i == "Asian"){
    mod_main_confi <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:asian_vrmemz+ 
                                        + poly(years_over_65, 2, raw = TRUE) + 
                                         W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                                       REML = FALSE, data = khandle1_long, subset = (W1_D_RACE_SUMMARY == i))
  
  } else if (i == "LatinX") {
     mod_main_confi <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:latin_vrmemz+ 
                                        + poly(years_over_65, 2, raw = TRUE) + 
                                         W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                                       REML = FALSE, data = khandle1_long, subset = (W1_D_RACE_SUMMARY == i))
  } else {
    mod_main_confi <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + poly(years_over_65, 2, raw = TRUE) + 
                                         W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                                       REML = FALSE, data = khandle1_long, subset = (W1_D_RACE_SUMMARY == i))
  }
  
  stargazer(summary(mod_main_confi)$coef, type = "text", title = paste("Confidante regression for", i,  "participants using main covariates"))
  
  tables_main_covars_confi[[i]] <- make_table(mod_main_confi)
}

saveRDS(tables_main_covars_confi, 'output/tables_main_covars_confi.RDS')
```

## Confidante models adjusting for all covariates

```{r conf full sample}
m_confidante_overall <- lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:asian_vrmemz + 
                                         confidante_bin:latin_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                                         W1_D_GENDER + W1_EDU_new_c + ADL_IADL + income_num_c + tot_drinks_week + retirement_stat + (1|STUDYID), 
                                       REML = FALSE, data = khandle1_long)

stargazer(summary(m_confidante_overall)$coeff, type = "text")

table2_confi <- make_table(m_confidante_overall)
saveRDS(table2_confi, 'output/table2_confi.RDS')

#adding interaction between confidante and race
m2_int_confi <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:W1_D_RACE_SUMMARY + 
                                 confidante_bin:asian_vrmemz + confidante_bin:latin_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                                 W1_D_GENDER + W1_EDU_new_c + ADL_IADL + income_num_c + tot_drinks_week + retirement_stat + (1|STUDYID),
                               REML = FALSE, data = khandle1_long)
anova(m2_int_confi)
```

### Stratified confidante models with all covariates

```{r}
tables_all_covars_confi <- list()

for(i in c("White", "Black", "LatinX", "Asian")){
  if(i == "Asian"){
    mod_all_confi <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:asian_vrmemz + 
                                      poly(years_over_65, 2, raw = TRUE) + 
                                      W1_D_GENDER + W1_EDU_new_c + ADL_IADL + income_num_c + tot_drinks_week + retirement_stat + (1|STUDYID), 
                                    REML = FALSE, data = khandle1_long, subset = (W1_D_RACE_SUMMARY == i))
    
  } else if (i == "LatinX") {
    mod_all_confi <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:latin_vrmemz+ 
                                      + poly(years_over_65, 2, raw = TRUE) + 
                                      W1_D_GENDER + W1_EDU_new_c + + ADL_IADL + income_num_c + tot_drinks_week + retirement_stat + (1|STUDYID), 
                                    REML = FALSE, data = khandle1_long, subset = (W1_D_RACE_SUMMARY == i))
  } else {
    mod_all_confi <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + 
                                      + poly(years_over_65, 2, raw = TRUE) + 
                                      W1_D_GENDER + W1_EDU_new_c + + ADL_IADL + income_num_c + tot_drinks_week + retirement_stat + (1|STUDYID), 
                                    REML = FALSE, data = khandle1_long, subset = (W1_D_RACE_SUMMARY == i))
  }
  
  #class(mod_all_confi) <- 'lmerMod'
  stargazer(summary(mod_all_confi)$coef, 
            #mod_all_confi, ci = T,
            type = "text", title = paste("Confidante regression for", i,  "participants using all covariates"))
  
  #tables_all_covars_confi[[i]] <- make_table(mod_all_confi)
}

saveRDS(tables_all_covars_confi, 'output/tables_all_covars_confi.RDS')
```

