---
title: "08_cross_sectional_analysis_impute"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#libraries & datasets
library(dplyr)
library(stargazer)
library(mice)
library(ggplot2)
library(tableone)
library(kableExtra)
library(tidyverse)
library(miceadds)

final_dat_both <- read.csv("/Users/ccalmasini/Desktop/Projects/social_networks_paper/social_nets_dat_both_waves.csv")
```

# Integration score models with imputed datasets

Generate 20 imputed datasets on the flat dataset, then turn each of them into long format and run the analysis. 

```{r}
#here i am imputing W1_EDU_new_c, income_num, ADL_IADL and tot_drinks_week
khandle_full <- final_dat_both %>%
  mutate(W1_EDU_new_c = W1_EDU_new - 12,
         W1_D_GENDER = case_when(W1_D_GENDER == 1 ~ "Male",
                                 W1_D_GENDER == 2 ~ "Female"),
         W1_D_GENDER = as.factor(W1_D_GENDER),
         W1_SMK = ifelse(W1_SMK == 0, "No", "Yes"),
         years_over_65 = W1_INTERVIEW_AGE - 65, 
         vrmemz = as.numeric(vrmemz),
         semz = as.numeric(semz),
         execz = as.numeric(execz),
         retirement_stat = as.factor(retirement_stat)) %>%
  dplyr::select(-c(X, W1_SMK, IADL, ADL, W1_INTERVIEW_AGE, W1_EDU_new, smk_status, vrmemz_w2, semz_w2, execz_w2, W2_INTERVIEW_AGE))

#making a predictor matrix to pick which variables are used in the multiple imputation models
pred <- data.frame(diag(ncol(khandle_full)))
pred <- 1-pred
colnames(pred) <- colnames(khandle_full)
rownames(pred) <- colnames(khandle_full)

vars_impute <- apply(is.na(khandle_full), 2, sum) > 0

pred[names(which(vars_impute == FALSE)), ] <- 0
pred[,1:6] <- 0

pred <- as.matrix(pred)

#20 imputatios on the flat dataset
imputations <- mice::mice(khandle_full, print = FALSE, seed = 123, 
                          pred = pred,
                          m=20)

#this gives a list with 20 datasets, one for each imputation
imp_dat <- mice::complete(imputations, "all")
```

```{r imputing main covariates models}
#making a for loop that loops through each element of imp_dat (ie each of the 20 imputed datasets)
#and turns the data into long format
#then runs the overall model and race-stratified models adjusted for covariates
#and returns lists of coefficients and standard errors

imp_coefs_main <- list()
stan_errs_main <- list()

#these models only use main covariates
for(i in 1:20){
 tmp_dat <- imp_dat[[i]]
  
  dat_long <- tmp_dat %>%
    mutate(income_num_c = scale(income_num, center = TRUE, scale = TRUE)) %>%
    gather(cognitive_test, cognitive_score, c(execz, vrmemz, semz)) %>%
    mutate(cognitive_test =  as.factor(cognitive_test),
           STUDYID = as.factor(STUDYID)) %>%
    unite(r_d, W1_D_RACE_SUMMARY, cognitive_test, remove = FALSE) %>%
    mutate(r_d = relevel(as.factor(r_d), ref = "Asian_execz"),
           asian_vrmemz = as.factor(ifelse(r_d == "Asian_vrmemz", 1, 0))) 
  
  mod <- lmerTest::lmer(cognitive_score ~ int_score + r_d + int_score:asian_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID),            
                       REML = FALSE, data = dat_long)
  
  mod_white <- lmerTest::lmer(cognitive_score ~ int_score + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID),           
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "White"))
  
  mod_latinx <- lmerTest::lmer(cognitive_score ~ int_score + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID),             
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "LatinX"))
  
  mod_black <- lmerTest::lmer(cognitive_score ~ int_score + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID),            
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "Black"))
  
  mod_asian <- lmerTest::lmer(cognitive_score ~ int_score + int_score:asian_vrmemz + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID),             
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "Asian"))
  
  imp_coefs_main$full_sample[[i]] <- summary(mod)$coef[2,1]
  stan_errs_main$full_sample[[i]] <- summary(mod)$coef[2,2]
  
  imp_coefs_main$white[[i]] <- summary(mod_white)$coef[2,1]
  stan_errs_main$white[[i]] <- summary(mod_white)$coef[2,2]
  
  imp_coefs_main$latinx[[i]] <- summary(mod_latinx)$coef[2,1]
  stan_errs_main$latinx[[i]] <- summary(mod_latinx)$coef[2,2]
  
  imp_coefs_main$black[[i]] <- summary(mod_black)$coef[2,1]
  stan_errs_main$black[[i]] <- summary(mod_black)$coef[2,2]
  
  imp_coefs_main$asian[[i]] <- summary(mod_asian)$coef[2,1]
  stan_errs_main$asian[[i]] <- summary(mod_asian)$coef[2,2]
}

#this calculates a pooled coefficient with standard errors for the MI 
#pooled coeff should just be average of all 20 coeffs from imputed datasets
#standard error should be sqrt(within variance+between variance)
#within variance = mean(standard errors from imputations^2)
#between variance = (1 + 1/19) * sd(coefficients from imputations)^2

imputed_coef_main <- list()

for (i in c('full_sample', 'asian', 'black', 'latinx', 'white')){
  pooled_coeff <- mean(unlist(imp_coefs_main[i]))
  within_var <- mean(unlist(stan_errs_main[i])**2)
  between_var <- (1 + 1/19) * sd(unlist(imp_coefs_main[i]))^2
  #between_var <- sum((unlist(imp_coefs_main[i]) - pooled_coeff)^2)/19

  #pooled error
  pooled_stand_err <- sqrt(within_var+between_var)
  
  lower_ci <- pooled_coeff - 1.96 * pooled_stand_err
  upper_ci <- pooled_coeff + 1.96 * pooled_stand_err

  imputed_coef_main[[i]] <- paste0(round(pooled_coeff, 3), " (", round(lower_ci, 3), ", ", round(upper_ci, 3), ")")
}

saveRDS(imputed_coef_main, 'output/imputed_coef_main.RDS')
```

```{r}
#same as above but with full covariate set
imp_coefs <- list()
stan_errs <- list()

for(i in 1:20){
 tmp_dat <- imp_dat[[i]]
  
  dat_long <- tmp_dat %>%
    mutate(income_num_c = scale(income_num, center = TRUE, scale = TRUE)) %>%
    gather(cognitive_test, cognitive_score, c(execz, vrmemz, semz)) %>%
    mutate(cognitive_test =  as.factor(cognitive_test),
           STUDYID = as.factor(STUDYID)) %>%
    unite(r_d, W1_D_RACE_SUMMARY, cognitive_test, remove = FALSE) %>%
    mutate(r_d = relevel(as.factor(r_d), ref = "Asian_execz"),
           asian_vrmemz = as.factor(ifelse(r_d == "Asian_vrmemz", 1, 0))) 
  
  mod <- lmerTest::lmer(cognitive_score ~ int_score + r_d + int_score:asian_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID),            
                       REML = FALSE, data = dat_long)
  
  mod_white <- lmerTest::lmer(cognitive_score ~ int_score + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + + retirement_stat + (1|STUDYID),           
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "White"))
  
  mod_latinx <- lmerTest::lmer(cognitive_score ~ int_score + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID),             
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "LatinX"))
  
  mod_black <- lmerTest::lmer(cognitive_score ~ int_score + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID),            
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "Black"))
  
  mod_asian <- lmerTest::lmer(cognitive_score ~ int_score + int_score:asian_vrmemz + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID),             
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "Asian"))
  
  imp_coefs$full_sample[[i]] <- summary(mod)$coef[2,1]
  stan_errs$full_sample[[i]] <- summary(mod)$coef[2,2]
  
  imp_coefs$white[[i]] <- summary(mod_white)$coef[2,1]
  stan_errs$white[[i]] <- summary(mod_white)$coef[2,2]
  
  imp_coefs$latinx[[i]] <- summary(mod_latinx)$coef[2,1]
  stan_errs$latinx[[i]] <- summary(mod_latinx)$coef[2,2]
  
  imp_coefs$black[[i]] <- summary(mod_black)$coef[2,1]
  stan_errs$black[[i]] <- summary(mod_black)$coef[2,2]
  
  imp_coefs$asian[[i]] <- summary(mod_asian)$coef[2,1]
  stan_errs$asian[[i]] <- summary(mod_asian)$coef[2,2]
}

imputed_coef_CI <- list()

for (i in c('full_sample', 'asian', 'black', 'latinx', 'white')){
  pooled_coeff <- mean(unlist(imp_coefs[i]))
  within_var <- mean(unlist(stan_errs[i])**2)
  between_var <- (1 + 1/19) * sd(unlist(imp_coefs[i]))^2
  
  #pooled error
  pooled_stand_err <- sqrt(within_var+between_var)
  
  lower_ci <- pooled_coeff - 1.96 * pooled_stand_err
  upper_ci <- pooled_coeff + 1.96 * pooled_stand_err

  imputed_coef_CI[[i]] <- paste0(round(pooled_coeff, 3), " (", round(lower_ci, 3), ", ", round(upper_ci, 3), ")")
}

saveRDS(imputed_coef_CI, 'output/imputed_coef_CI.RDS')
```

### Calculating pooled p vals from F-tests (using micombine.F function)

1. Main covariate set  

```{r}
f <- c()
for(i in 1:20){
  print(i)
  tmp_dat <- imp_dat[[i]]
  
  dat_long <- tmp_dat %>%
    mutate(income_num_c = scale(income_num, center = TRUE, scale = TRUE)) %>%
    gather(cognitive_test, cognitive_score, c(execz, vrmemz, semz)) %>%
    mutate(cognitive_test =  as.factor(cognitive_test),
           STUDYID = as.factor(STUDYID)) %>%
    unite(r_d, W1_D_RACE_SUMMARY, cognitive_test, remove = FALSE) %>%
    mutate(r_d = relevel(as.factor(r_d), ref = "Asian_execz"),
           asian_vrmemz = as.factor(ifelse(r_d == "Asian_vrmemz", 1, 0))) 
  
  m_int<- lmerTest::lmer(cognitive_score ~ int_score + r_d + int_score:W1_D_RACE_SUMMARY + 
                             int_score:asian_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                           REML = FALSE, data = dat_long)
  
  anv <- data.frame(anova(m_int))
  f[i] <- anv["int_score:W1_D_RACE_SUMMARY", 'F.value']
}

micombine.F(f, df1=3)

```

2. Full covariate set 

```{r}
f_all <- c()
p_all <- c()
for(i in 1:20){
  print(i)
  tmp_dat <- imp_dat[[i]]
  
  dat_long <- tmp_dat %>%
    mutate(income_num_c = scale(income_num, center = TRUE, scale = TRUE)) %>%
    gather(cognitive_test, cognitive_score, c(execz, vrmemz, semz)) %>%
    mutate(cognitive_test =  as.factor(cognitive_test),
           STUDYID = as.factor(STUDYID)) %>%
    unite(r_d, W1_D_RACE_SUMMARY, cognitive_test, remove = FALSE) %>%
    mutate(r_d = relevel(as.factor(r_d), ref = "Asian_execz"),
           asian_vrmemz = as.factor(ifelse(r_d == "Asian_vrmemz", 1, 0))) 
  
  m_int<- lmerTest::lmer(cognitive_score ~ int_score + r_d + int_score:W1_D_RACE_SUMMARY + 
                           int_score:asian_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                           W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + 
                           retirement_stat + (1|STUDYID),            
                         REML = FALSE, data = dat_long)
  
  anv <- data.frame(anova(m_int))
  f_all[i] <- anv["int_score:W1_D_RACE_SUMMARY", 'F.value']
  p_all[i] <- anv["int_score:W1_D_RACE_SUMMARY", 'Pr..F.']
}

micombine.F(f_all, df1=3)
```

# Confidante models with imputed dataset

```{r}
#same as above -- but now imputing running models for confidante using main covariates

imp_coefs_confi_main <- list()
stan_errs_main_confi <- list()

for(i in 1:20){
 tmp_dat <- imp_dat[[i]]
  
  dat_long <- tmp_dat %>%
    mutate(income_num_c = scale(income_num, center = TRUE, scale = TRUE)) %>%
    gather(cognitive_test, cognitive_score, c(execz, vrmemz, semz)) %>%
    mutate(cognitive_test =  as.factor(cognitive_test),
           STUDYID = as.factor(STUDYID)) %>%
    unite(r_d, W1_D_RACE_SUMMARY, cognitive_test, remove = FALSE) %>%
    mutate(r_d = relevel(as.factor(r_d), ref = "Asian_execz"),
           asian_vrmemz = as.factor(ifelse(r_d == "Asian_vrmemz", 1, 0)),
         latin_vrmemz = as.factor(ifelse(r_d == "LatinX_vrmemz", 1, 0))) 
  
  mod <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:asian_vrmemz + confidante_bin:latin_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID),                        
                       REML = FALSE, data = dat_long)
  
  mod_white <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + (1|STUDYID),                        
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "White"))
  
  mod_latinx <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:latin_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID),                        
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "LatinX"))
  
  mod_black <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID),                        
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "Black"))
  
  mod_asian <- lmerTest::lmer(cognitive_score ~ confidante_bin + confidante_bin:asian_vrmemz + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + (1|STUDYID),                        
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "Asian"))
  
  imp_coefs_confi_main$full_sample[[i]] <- summary(mod)$coef[2,1]
  stan_errs_main_confi$full_sample[[i]] <- summary(mod)$coef[2,2]
  
  imp_coefs_confi_main$white[[i]] <- summary(mod_white)$coef[2,1]
  stan_errs_main_confi$white[[i]] <- summary(mod_white)$coef[2,2]
  
  imp_coefs_confi_main$latinx[[i]] <- summary(mod_latinx)$coef[2,1]
  stan_errs_main_confi$latinx[[i]] <- summary(mod_latinx)$coef[2,2]
  
  imp_coefs_confi_main$black[[i]] <- summary(mod_black)$coef[2,1]
  stan_errs_main_confi$black[[i]] <- summary(mod_black)$coef[2,2]
  
  imp_coefs_confi_main$asian[[i]] <- summary(mod_asian)$coef[2,1]
  stan_errs_main_confi$asian[[i]] <- summary(mod_asian)$coef[2,2]
}

imputed_coef_confi_main <- list()

for (i in c('full_sample', 'asian', 'black', 'latinx', 'white')){
  pooled_coeff <- mean(unlist(imp_coefs_confi_main[i]))
  within_var <- mean(unlist(stan_errs_main_confi[i])**2)
  between_var <- (1 + 1/19) * sd(unlist(imp_coefs_confi_main[i]))^2

  #pooled error
  pooled_stand_err <- sqrt(within_var+between_var)
  
  lower_ci <- pooled_coeff - 1.96 * pooled_stand_err
  upper_ci <- pooled_coeff + 1.96 * pooled_stand_err

  imputed_coef_confi_main[[i]] <- paste0(round(pooled_coeff, 3), " (", round(lower_ci, 3), ", ", round(upper_ci, 3), ")")
}

saveRDS(imputed_coef_confi_main, 'output/imputed_coef_confi_main.RDS')
```

```{r}
#same as above -- but now imputing for confidante running models for confidante using all covariates
imp_coefs_confi <- list()
stan_errs_confi <- list()

for(i in 1:20){
 tmp_dat <- imp_dat[[i]]
  
  dat_long <- tmp_dat %>%
    mutate(income_num_c = scale(income_num, center = TRUE, scale = TRUE)) %>%
    gather(cognitive_test, cognitive_score, c(execz, vrmemz, semz)) %>%
    mutate(cognitive_test =  as.factor(cognitive_test),
           STUDYID = as.factor(STUDYID)) %>%
    unite(r_d, W1_D_RACE_SUMMARY, cognitive_test, remove = FALSE) %>%
    mutate(r_d = relevel(as.factor(r_d), ref = "Asian_execz"),
           asian_vrmemz = as.factor(ifelse(r_d == "Asian_vrmemz", 1, 0)),
         latin_vrmemz = as.factor(ifelse(r_d == "LatinX_vrmemz", 1, 0))) 
  
  mod <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:asian_vrmemz + confidante_bin:latin_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID),                        
                       REML = FALSE, data = dat_long)
  
  mod_white <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID),                        
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "White"))
  
  mod_latinx <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:latin_vrmemz + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID),                        
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "LatinX"))
  
  mod_black <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID),                        
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "Black"))
  
  mod_asian <- lmerTest::lmer(cognitive_score ~ confidante_bin + confidante_bin:asian_vrmemz + r_d + poly(years_over_65, 2, raw = TRUE) + 
                       W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + retirement_stat + (1|STUDYID),                        
                       REML = FALSE, data = dat_long, subset = (W1_D_RACE_SUMMARY == "Asian"))
  
  imp_coefs_confi$full_sample[[i]] <- summary(mod)$coef[2,1]
  stan_errs_confi$full_sample[[i]] <- summary(mod)$coef[2,2]
  
  imp_coefs_confi$white[[i]] <- summary(mod_white)$coef[2,1]
  stan_errs_confi$white[[i]] <- summary(mod_white)$coef[2,2]
  
  imp_coefs_confi$latinx[[i]] <- summary(mod_latinx)$coef[2,1]
  stan_errs_confi$latinx[[i]] <- summary(mod_latinx)$coef[2,2]
  
  imp_coefs_confi$black[[i]] <- summary(mod_black)$coef[2,1]
  stan_errs_confi$black[[i]] <- summary(mod_black)$coef[2,2]
  
  imp_coefs_confi$asian[[i]] <- summary(mod_asian)$coef[2,1]
  stan_errs_confi$asian[[i]] <- summary(mod_asian)$coef[2,2]
}

imputed_coef_CI_confi <- list()

for (i in c('full_sample', 'asian', 'black', 'latinx', 'white')){
  pooled_coeff <- mean(unlist(imp_coefs_confi[i]))
  within_var <- mean(unlist(stan_errs_confi[i])**2)
  between_var <- (1 + 1/19) * sd(unlist(imp_coefs_confi[i]))^2

  #pooled error
  pooled_stand_err <- sqrt(within_var+between_var)
  
  lower_ci <- pooled_coeff - 1.96 * pooled_stand_err
  upper_ci <- pooled_coeff + 1.96 * pooled_stand_err

  imputed_coef_CI_confi[[i]] <- paste0(round(pooled_coeff, 3), " (", round(lower_ci, 3), ", ", round(upper_ci, 3), ")")
}

saveRDS(imputed_coef_CI_confi, 'output/imputed_coef_CI_confi.RDS')
```

### Calculating pooled p vals from F-tests (using micombine.F function)

1. Main covariate set  

```{r}
f_conf <- c()
for(i in 1:20){
  print(i)
  tmp_dat <- imp_dat[[i]]
  
  dat_long <- tmp_dat %>%
    mutate(income_num_c = scale(income_num, center = TRUE, scale = TRUE)) %>%
    gather(cognitive_test, cognitive_score, c(execz, vrmemz, semz)) %>%
    mutate(cognitive_test =  as.factor(cognitive_test),
           STUDYID = as.factor(STUDYID)) %>%
    unite(r_d, W1_D_RACE_SUMMARY, cognitive_test, remove = FALSE) %>%
    mutate(r_d = relevel(as.factor(r_d), ref = "Asian_execz"),
           asian_vrmemz = as.factor(ifelse(r_d == "Asian_vrmemz", 1, 0)),
           latin_vrmemz = as.factor(ifelse(r_d == "LatinX_vrmemz", 1, 0))) 
    
  m_int <- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:W1_D_RACE_SUMMARY + 
                           confidante_bin:asian_vrmemz + 
                           confidante_bin:latin_vrmemz + poly(years_over_65, 2, raw = TRUE) +
                           W1_D_GENDER + W1_EDU_new_c + (1|STUDYID), 
                         REML = FALSE, data = dat_long)
  
  anv <- data.frame(anova(m_int))
  f_conf[i] <- anv["confidante_bin:W1_D_RACE_SUMMARY", 'F.value']
}

micombine.F(f_conf, df1=3)
```

2. Full covariate set 

```{r}
f_conf_all <- c()
for(i in 1:20){
  print(i)
  tmp_dat <- imp_dat[[i]]
  
  dat_long <- tmp_dat %>%
    mutate(income_num_c = scale(income_num, center = TRUE, scale = TRUE)) %>%
    gather(cognitive_test, cognitive_score, c(execz, vrmemz, semz)) %>%
    mutate(cognitive_test =  as.factor(cognitive_test),
           STUDYID = as.factor(STUDYID)) %>%
    unite(r_d, W1_D_RACE_SUMMARY, cognitive_test, remove = FALSE) %>%
    mutate(r_d = relevel(as.factor(r_d), ref = "Asian_execz"),
           asian_vrmemz = as.factor(ifelse(r_d == "Asian_vrmemz", 1, 0)),
           latin_vrmemz = as.factor(ifelse(r_d == "LatinX_vrmemz", 1, 0))) 
    
  m_int<- lmerTest::lmer(cognitive_score ~ confidante_bin + r_d + confidante_bin:W1_D_RACE_SUMMARY + 
                           confidante_bin:asian_vrmemz + confidante_bin:latin_vrmemz + poly(years_over_65, 2, raw = TRUE) +
                           W1_D_GENDER + W1_EDU_new_c + ADL_IADL + tot_drinks_week + income_num_c + 
                           retirement_stat + (1|STUDYID),                        
                         REML = FALSE, data = dat_long)
  
  anv <- data.frame(anova(m_int))
  f_conf_all[i] <- anv["confidante_bin:W1_D_RACE_SUMMARY", 'F.value']
}

micombine.F(f_conf_all, df1=3)
```














